---
title: "RBingAds - R interface for the Bing Ads API"
author: "Johannes Burkhardt"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{RBingAds - R interface for the Bing Ads API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Introduction

Welcome to the official documentation of the **RBingAds** package for **Bing Ads**. RBingAds enables users of the R Language for Statistical Computing to directly access their Bing Ads account in order to consume and analyze information provided by the Bing Ads API.

### Requirements

In order to use the **RBingAds** package, you need access to the **Bing Ads API**. You will need following credentials and information:

- client id
- client secret
- API developer token
- admin email login with password
- customer / manager id
- account id

### Installation

```{r installation, eval=FALSE}
require(devtools)
install_github("jburkhardt/RBingAds")
```

### Bing Ads API Authentication

The authentication requires a **client id**, a **client secret** and the **API developer token** from the API project (app, SDK). Furthermore, you need an **admin email** with **login credentials / password** for a one time authentication including user interaction in the webbrowser.

```{r authentication, eval=FALSE}
library(RBingAds)
bing_auth <- authenticate(save = T)
```

### Load Data

Loading data proceedes in three steps:

1. Generating a report id
2. Get a download url
3. Download the data

#### Generate Report ID

```{r report_id, eval=FALSE}
report_id <- get_report_id(bing_auth = bing_auth,
                           customer_id = "*******",
                           account_id = "*******",
                           report = "CampaignPerformanceReport",
                           columns = c("AccountName", "CampaignName", "TimePeriod", "Impressions", "Clicks", "Spend", "Conversions"),
                           start = "2019-01-01",
                           end = "2019-01-31")
```

#### Get Download URL

```{r download_url, eval=FALSE}
download_url <- get_download_url(bing_auth = bing_auth,
                                customer_id = "******",
                                account_id = "*******",
                                report_id = report_id)
```

#### Download Data

```{r download_data, eval=FALSE}
data <- download_data(download_url = download_url)
```

### Acknowledgement

I would like to express my deep gratitude to [Deepesh Goel](https://github.com/deepeshgoeliitk). His previous work on the Bing Ads API and related xml parsing was the key to develop this package.
